STAT 133 Final Project: Visualizing Berkeley Police Data

### 2016-08-09 final_paper/finalpaper.Rmd
git figure

```{r, warning = FALSE, echo = F, fig.width = 10, fig.height = 5, message = FALSE, fig.align="center"}
grid.arrange(map_stop1,map_callservice1, ncol = 2)
```

@@

```{r, warning = FALSE, echo = F, fig.width = 10, fig.height = 5, message = FALSE, fig.align="center"}
grid.arrange(stopdensitymap4, popdenmap, ncol=2)
```

@@

```{r, fig.height = 3, fig.width = 12, echo=FALSE, warning = FALSE, message = FALSE, fig.align="center"}
stopdensitymap3 
```

@@

```{r, warning = FALSE, echo = FALSE,  fig.width = 15, fig.height = 3, message = FALSE, fig.align = "center"}
grid.arrange(a2,black2,h2,o2,w2, ncol = 5) # print population density by race.
```

@@

A visualization of the groups of people stopped in proportion to their population is provided by the bar chart below.
```{r, message = F, echo = FALSE, fig.width = 10, fig.height = 3, warning = FALSE, fig.align="center"}
grid.arrange(bargraph1, bargraph2, ncol = 2)
```

@@

```{r, echo=FALSE, warning = FALSE, message=FALSE, fig.align = "center", fig.width = 8, fig.height = 3}
map_enforcement
```

@@

```{r, fig.height = 5, fig.width = 10, echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
map_reasons1
```

@@

```{r, fig.height = 3, fig.width = 10, echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_arrest
```
## PLEASE EDIT THE ANALYSIS 
###  LOVE JENNY 
From the above plots, we can tell that the probability of arrested in a stop with the reason Traffic is much lower than other reasons. The average conditional probability of arrested given reason is traffic is 1.58%. Additionally, the probability of arrested in a stop with the reason Wanted is much higher than other reason. The average conditional probability of arrested given reason is wanted is 33.33%. Lastly, an interesting fact is that the conditional probability of arrested in a stop with the reason Probation or Parole and race Asian is 75%, which is much higher than that of any other race. Asian people is much more liable to be arrested by Berkeley Police Department during Probation or Parole if stopped by the BPD.

```{r, fig.height = 3, fig.width = 10, echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_arrest_age
```

@@

```{r, fig.height = 3, fig.width = 10, echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_arrest_gender
```

@@

```{r, fig.height = 3, fig.width = 10, echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_percentage3
```
##  Findings 
#### LOVE JENNY
Black people are obviously liable to commit incidents at night. The average ratio of black people to all people stoped by the Berkeley Police Department at night is about 40%. On the other hand, white people are obviously liable to commit incidents in the daytime. The average ratio of white people to all people stoped by the Berkeley Police Deparment during the day is about 45%. While the Ratio of incidents commited by Asian people, Hispanic people and other people fluctuate during the daytime and the night, with an average ratio of 8%, 11% and 9% respectively.

```{r, fig.height = 3, fig.width = 10, echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_percentage2
```

@@

```{r, echo=FALSE, warning = FALSE, message=FALSE, fig.height = 3, fig.width = 10, fig.align="center"}
grid.arrange(bararrest, barjail, ncol = 2)
```

>>>>

```{r, warning = FALSE, echo = F, fig.width = 10, fig.height = 5, message = FALSE, fig.align="center", fig.cap= "BP stop and Calls for service"}
grid.arrange(map_stop1,map_callservice1, ncol = 2)
```

@@

```{r, warning = FALSE, echo = F, fig.width = 10, fig.height = 5, message = FALSE, fig.align="center", fig.cap= "Berkeley Police Stop Density Map by Race"}
grid.arrange(stopdensitymap4, popdenmap, ncol=2)
```

@@

```{r, fig.height = 3, fig.width = 12, echo=FALSE, warning = FALSE, message = FALSE, fig.align="center", fig.cap= "Police Stop density map VS. Population Density"}
stopdensitymap3 
```

@@

```{r, warning = FALSE, echo = FALSE,  fig.width = 15, fig.height = 3, message = FALSE, fig.align = "center", fig.cap= "Berkeley Population Density Map by Race"}
grid.arrange(a2,black2,h2,o2,w2, ncol = 5) # print population density by race.
```

@@

A visualization of the groups of people stopped in proportion to their population is provided by the bar chart below.
```{r, message = F, echo = FALSE, fig.width = 10, fig.height = 3, warning = FALSE, fig.align="center", fig.cap= "Percent stopped and Perecent Population Stopped"}
grid.arrange(bargraph1, bargraph2, ncol = 2)
```

@@

```{r, echo=FALSE, warning = FALSE, message=FALSE, fig.cap= "Police Stops Leading to Arrests", fig.align = "center", fig.width = 8, fig.height = 3}
map_enforcement
```

@@

```{r, fig.height = 5, fig.width = 10, fig.cap= "Police Stops by Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
map_reasons1
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Probability of Arrested by BDP Race VS Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_arrest
```
## PLEASE EDIT THE ANALYSIS 
###  LOVE JENNY 
From the above plots, we can tell that the probability of arrested in a stop with the reason Traffic is much lower than other reasons. The average conditional probability of arrested given reason is traffic is 1.58%. Additionally, the probability of arrested in a stop with the reason Wanted is much higher than other reason. The average conditional probability of arrested given reason is wanted is 33.33%. Lastly, an interesting fact is that the conditional probability of arrested in a stop with the reason Probation or Parole and race Asian is 75%, which is much higher than that of any other race. Asian people is much more liable to be arrested by Berkeley Police Department during Probation or Parole if stopped by the BPD.

```{r, fig.height = 3, fig.width = 10, fig.cap= "Probability of Arrested by BDP Age VS Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_arrest_age
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Probability of Arrested by BDP Gender VS Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_arrest_gender
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Probability of Arrested by BDP Race VS Hour", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_percentage3
```
##  Findings 
#### LOVE JENNY
Black people are obviously liable to commit incidents at night. The average ratio of black people to all people stoped by the Berkeley Police Department at night is about 40%. On the other hand, white people are obviously liable to commit incidents in the daytime. The average ratio of white people to all people stoped by the Berkeley Police Deparment during the day is about 45%. While the Ratio of incidents commited by Asian people, Hispanic people and other people fluctuate during the daytime and the night, with an average ratio of 8%, 11% and 9% respectively.

```{r, fig.height = 3, fig.width = 10, fig.cap= "Probability of Arrested by BDP Age VS Hour", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_percentage2
```

@@

```{r, echo=FALSE, fig.cap= "Percentage of being arrested and being jailed", warning = FALSE, message=FALSE, fig.height = 3, fig.width = 10, fig.align="center"}
grid.arrange(bararrest, barjail, ncol = 2)
```
